---
title: "gtsummary in quarto"
format: html
---

We are using some data from the longitudinal study....


```{r}
library(tidyverse)
library(gtsummary)

nlsy_cols <- c("glasses", "eyesight", "sleep_wkdy", "sleep_wknd", 
               "id", "nsibs", "samp", "race_eth", "sex", "region", 
               "income", "res_1980", "res_2002", "age_bir")
nlsy <- read_csv(here::here("data", "raw", "nlsy.csv"), 
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
                 skip = 1, col_names = nlsy_cols) |> 
  mutate(region_cat = factor(region, labels = c("Northeast", "North Central", "South", "West")),
         sex_cat = factor(sex, labels = c("Male", "Female")),
         race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic")),
         eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
         glasses_cat = factor(glasses, labels = c("No", "Yes"))) 
```

# Customization of `tbl_summary()`

@tbl-one contains a table 

There were `r 3+4` participants


```{r}
#| label: tbl-one
#| tbl-cap: "This is a great table"
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```


This is the number of people in the data
```{r}
nrow(nlsy)
```

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir),
  label = list(
    race_eth_cat ~ "Race/ethnicity",
    region_cat ~ "Region",
    eyesight_cat ~ "Eyesight",
    glasses ~ "Wears glasses",
    age_bir ~ "Age at first birth"
  ),
  missing_text = "Missing")
```

```{r}
#| label: last table 
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

#storing as object (mean or median- just need to replace one with the other )
```{r}
median_sleep_weekends<-median(nlsy$sleep_wknd, na.rm = TRUE)

```

#inline text
The average number of hours of sleep on weekends is `r median_sleep_weekends`.


#inline text
The average number of hours of sleep on weekends is `r median(nlsy$sleep_wknd, na.rm = TRUE)`


#dif table two to play with

```{r}
#| label: tbl-two 
#| tbl-cap: "This is a great table"
table2<-tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir, sleep_wknd)) |>
	
	add_overall() #adds overall combining Male and Female 

table2
```




```{r}
sleep_wknd_f<-inline_text(table2, variable="sleep_wknd", column= "stat_0")

inline_text(table2, variable="sleep_wknd", column= "stat_0")

```

The median number of hours of sleep and the IQR on weekends in the overall sample is `r sleep_wknd_f`.


